Convolutional Neural Networks and Volcano Plots: Screening and Prediction of Two-Dimensional Single-Atom Catalysts for CO\textsubscript{2} Reduction Reactions

### 2024-01-14 paper/arxiv/si_3_ml.tex
replace curly quotes

The format of the 2D array for the eDOS is naturally well-suited for use as neural network inputs.
In this study, the array adopts a shape of [numSamplings, numOrbitals, numChannels], as illustrated in \cref{si_fig20:input_dos}.
Here, “numSamplings” represents the number of data points sampled across the energy spectrum,
“numOrbitals” denotes the number of DOS orbitals,
and “numChannels” indicates the number of atomic channels.

@@

% Supplementary Table 18: Prediction MAEs of the CNN model
\begin{table}[htbp]
  \centering
  \begin{tabular}{lll}
    \toprule
    Adsorbate             & Original dataset (eV) & Augmented dataset (eV) \\
    \midrule
    CO\textsubscript{2}   & 0.0447 & 0.0336 \\
    COOH                  & 0.0436 & 0.0581 \\
    CO                    & 0.0402 & 0.0402 \\
    CHO                   & 0.0614 & 0.0778 \\
    CH\textsubscript{2}O  & 0.0553 & 0.0632 \\
    OCH\textsubscript{3}  & 0.0605 & 0.0636 \\
    O                     & 0.1135 & 0.1081 \\
    OH                    & 0.0547 & 0.0602 \\
    H                     & 0.0703 & 0.0646 \\
    \bottomrule
  \end{tabular}
  \caption{Prediction mean absolute errors of the CNN model}
  \tablefootnote{The same CNN model, trained on the augmented dataset, was used for all predictions.
  The term “original dataset” refers to evaluations conducted on the original dataset without any augmented data;
  it does not imply the use of a different CNN model trained solely on the original dataset.
  Similarly, “augmented dataset” refers to evaluations on the dataset with both original data and augment data,
  not a distinct model.}
  \label{si_table18:cnn_mae}
\end{table}

@@

% SI Figure 21: Illustration of the eDOS occlusion experiment
\begin{figure}[htbp]
  \centering
  \includegraphics[width=\textwidth]{si_fig21_occlusion.png}
  \caption{\textbf{Illustration of the eDOS occlusion experiment.}
  This figure demonstrates the step-by-step process of the occlusion experiment.
  The input eDOS array first undergoes zero-padded, and then a masker of width “width” is applied,
  resulting in an occlusion array that preserves the shape of the input array.}
  \label{si_fig21:occlusion}
\end{figure}

% SI Figure 22: Occlusion experiment with a masker width of 1
\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.6\textwidth]{si_fig22_occl_wid1.png}
  \caption{\textbf{Occlusion Experiment with a masker width of “1”.}
  This figure shows an occlusion experiment on the Ge atom in
  the initial state of CO adsorption on Ge@g-C\textsubscript{3}N\textsubscript{4}.}
  \label{si_fig22:occl_wid1}
\end{figure}

% SI Figure 23: Occlusion experiment with a masker width of 3
\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.6\textwidth]{si_fig23_occl_wid3.png}
  \caption{\textbf{Occlusion Experiment with a masker width of “3”.}
  This figure shows an occlusion experiment on the Ge atom in
  the initial state of CO adsorption on Ge@g-C\textsubscript{3}N\textsubscript{4}.}
  \label{si_fig23:occl_wid3}
\end{figure}

% SI Figure 24: Occlusion experiment with a masker width of 5
\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.6\textwidth]{si_fig24_occl_wid5.png}
  \caption{\textbf{Occlusion Experiment with a masker width of “5”.}
  This figure shows an occlusion experiment on the Ge atom in
  the initial state of CO adsorption on Ge@g-C\textsubscript{3}N\textsubscript{4}.}
  \label{si_fig24:occl_wid5}
\end{figure}

% SI Figure 25: Occlusion experiment with a masker width of 11
\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.6\textwidth]{si_fig25_occl_wid11.png}
  \caption{\textbf{Occlusion Experiment with a masker width of “11”.}
  This figure shows an occlusion experiment on the Ge atom in
  the initial state of CO adsorption on Ge@g-C\textsubscript{3}N\textsubscript{4}.}
  \label{si_fig25:occl_wid11}
\end{figure}

% SI Figure 26: Occlusion experiment with a masker width of 21
\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.6\textwidth]{si_fig26_occl_wid21.png}
  \caption{\textbf{Occlusion Experiment with a masker width of “21”.}
  This figure shows an occlusion experiment on the Ge atom in
  the initial state of CO adsorption on Ge@g-C\textsubscript{3}N\textsubscript{4}.}
  \label{si_fig26:occl_wid21}
\end{figure}

% SI Figure 27: Occlusion experiment with a masker width of 31
\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.6\textwidth]{si_fig27_occl_wid31.png}
  \caption{\textbf{Occlusion Experiment with a masker width of “31”.}
  This figure shows an occlusion experiment on the Ge atom in
  the initial state of CO adsorption on Ge@g-C\textsubscript{3}N\textsubscript{4}.}
  \label{si_fig27:occl_wid31}
\end{figure}

% SI Figure 28: Occlusion experiment with a masker width of 41
\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.6\textwidth]{si_fig28_occl_wid41.png}
  \caption{\textbf{Occlusion Experiment with a masker width of “41”.}
  This figure shows an occlusion experiment on the Ge atom in
  the initial state of CO adsorption on Ge@g-C\textsubscript{3}N\textsubscript{4}.}
  \label{si_fig28:occl_wid41}
\end{figure}

% SI Figure 29: Occlusion experiment with a masker width of 51
\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.6\textwidth]{si_fig29_occl_wid51.png}
  \caption{\textbf{Occlusion Experiment with a masker width of “51”.}
  This figure shows an occlusion experiment on the Ge atom in
  the initial state of CO adsorption on Ge@g-C\textsubscript{3}N\textsubscript{4}.}
  \label{si_fig29:occl_wid51}
\end{figure}

>>>>

The format of the 2D array for the eDOS is naturally well-suited for use as neural network inputs.
In this study, the array adopts a shape of [numSamplings, numOrbitals, numChannels], as illustrated in \cref{si_fig20:input_dos}.
Here, "numSamplings" represents the number of data points sampled across the energy spectrum,
"numOrbitals" denotes the number of DOS orbitals,
and "numChannels" indicates the number of atomic channels.

@@

% Supplementary Table 18: Prediction MAEs of the CNN model
\begin{table}[htbp]
  \centering
  \begin{tabular}{lll}
    \toprule
    Adsorbate             & Original dataset (eV) & Augmented dataset (eV) \\
    \midrule
    CO\textsubscript{2}   & 0.0447 & 0.0336 \\
    COOH                  & 0.0436 & 0.0581 \\
    CO                    & 0.0402 & 0.0402 \\
    CHO                   & 0.0614 & 0.0778 \\
    CH\textsubscript{2}O  & 0.0553 & 0.0632 \\
    OCH\textsubscript{3}  & 0.0605 & 0.0636 \\
    O                     & 0.1135 & 0.1081 \\
    OH                    & 0.0547 & 0.0602 \\
    H                     & 0.0703 & 0.0646 \\
    \bottomrule
  \end{tabular}
  \caption{Prediction mean absolute errors of the CNN model}
  \tablefootnote{The same CNN model, trained on the augmented dataset, was used for all predictions.
  The term "original dataset" refers to evaluations conducted on the original dataset without any augmented data;
  it does not imply the use of a different CNN model trained solely on the original dataset.
  Similarly, "augmented dataset" refers to evaluations on the dataset with both original data and augment data,
  not a distinct model.}
  \label{si_table18:cnn_mae}
\end{table}

@@

% SI Figure 21: Illustration of the eDOS occlusion experiment
\begin{figure}[htbp]
  \centering
  \includegraphics[width=\textwidth]{si_fig21_occlusion.png}
  \caption{\textbf{Illustration of the eDOS occlusion experiment.}
  This figure demonstrates the step-by-step process of the occlusion experiment.
  The input eDOS array first undergoes zero-padded, and then a masker of width "width" is applied,
  resulting in an occlusion array that preserves the shape of the input array.}
  \label{si_fig21:occlusion}
\end{figure}

% SI Figure 22: Occlusion experiment with a masker width of 1
\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.6\textwidth]{si_fig22_occl_wid1.png}
  \caption{\textbf{Occlusion Experiment with a masker width of "1".}
  This figure shows an occlusion experiment on the Ge atom in
  the initial state of CO adsorption on Ge@g-C\textsubscript{3}N\textsubscript{4}.}
  \label{si_fig22:occl_wid1}
\end{figure}

% SI Figure 23: Occlusion experiment with a masker width of 3
\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.6\textwidth]{si_fig23_occl_wid3.png}
  \caption{\textbf{Occlusion Experiment with a masker width of "3".}
  This figure shows an occlusion experiment on the Ge atom in
  the initial state of CO adsorption on Ge@g-C\textsubscript{3}N\textsubscript{4}.}
  \label{si_fig23:occl_wid3}
\end{figure}

% SI Figure 24: Occlusion experiment with a masker width of 5
\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.6\textwidth]{si_fig24_occl_wid5.png}
  \caption{\textbf{Occlusion Experiment with a masker width of "5".}
  This figure shows an occlusion experiment on the Ge atom in
  the initial state of CO adsorption on Ge@g-C\textsubscript{3}N\textsubscript{4}.}
  \label{si_fig24:occl_wid5}
\end{figure}

% SI Figure 25: Occlusion experiment with a masker width of 11
\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.6\textwidth]{si_fig25_occl_wid11.png}
  \caption{\textbf{Occlusion Experiment with a masker width of "11".}
  This figure shows an occlusion experiment on the Ge atom in
  the initial state of CO adsorption on Ge@g-C\textsubscript{3}N\textsubscript{4}.}
  \label{si_fig25:occl_wid11}
\end{figure}

% SI Figure 26: Occlusion experiment with a masker width of 21
\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.6\textwidth]{si_fig26_occl_wid21.png}
  \caption{\textbf{Occlusion Experiment with a masker width of "21".}
  This figure shows an occlusion experiment on the Ge atom in
  the initial state of CO adsorption on Ge@g-C\textsubscript{3}N\textsubscript{4}.}
  \label{si_fig26:occl_wid21}
\end{figure}

% SI Figure 27: Occlusion experiment with a masker width of 31
\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.6\textwidth]{si_fig27_occl_wid31.png}
  \caption{\textbf{Occlusion Experiment with a masker width of "31".}
  This figure shows an occlusion experiment on the Ge atom in
  the initial state of CO adsorption on Ge@g-C\textsubscript{3}N\textsubscript{4}.}
  \label{si_fig27:occl_wid31}
\end{figure}

% SI Figure 28: Occlusion experiment with a masker width of 41
\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.6\textwidth]{si_fig28_occl_wid41.png}
  \caption{\textbf{Occlusion Experiment with a masker width of "41".}
  This figure shows an occlusion experiment on the Ge atom in
  the initial state of CO adsorption on Ge@g-C\textsubscript{3}N\textsubscript{4}.}
  \label{si_fig28:occl_wid41}
\end{figure}

% SI Figure 29: Occlusion experiment with a masker width of 51
\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.6\textwidth]{si_fig29_occl_wid51.png}
  \caption{\textbf{Occlusion Experiment with a masker width of "51".}
  This figure shows an occlusion experiment on the Ge atom in
  the initial state of CO adsorption on Ge@g-C\textsubscript{3}N\textsubscript{4}.}
  \label{si_fig29:occl_wid51}
\end{figure}
